Using the .R script version of the assignment is probably better since they can just put code in wherever.
(DON'T ASSIGN USING THE MARKDOWN DOCUMENT)

---
title: "3-Assignment: Answers - Manage and Manipulate Data"
subtitle: BIOL 5000
output:
  pdf_document: default #prevents ability to download .rmd file in html notebook
  html_notebook: default # don't use for distribution; tibble is truncated in html view
---
```{r setup, message=FALSE}
library(dplyr)
library(data.table) #might need to install if not on your computer
```
First load a dataset to work with;
```{r}
data(mtcars)
```
Where does this data come from? Is it magic?
For reference:  library(help = "datasets")

Fix problem with car names not being in a dataframe column
```{r}
mtcar_data <- data.table(mtcars, keep.rownames = TRUE) #can obviously use your 
#object name rather than data
mtcar_data <- rename(mtcar_data, name = rn)
mtcar_data #shows dataframe with the car names in first column
```

1. How to programmatically view the 'mtcars' dataset?
```{r}
quest_1 <- View(mtcars)
```
2. How do you determine the different types of data contained in mtcars?
```{r}
#str(datafrme)
quest_2 <- glimpse(dataframe)
```
3. Assign the mtcars dataset to a new object.
```{r}
quest_3 <-mtcars
```
Using our knowledge of dplyr, answer the following:
I recommend using 'pipes' where possible (but not required), as they are more intuitive.
Assign each answer to a new object (e.g. quest4, quest5, etc.)

4. What is the mean and standard deviation of horsepower (hp) for each group of cars, 
as measured by their number of cylinders (cyl)?
```{r quest4}
quest4 <- summarise(group_by(mtcars, cyl), mean(hp), sd(hp))
quest4
```
5. Of the cars having 8 cylinders, which six have the most horsepower? (show just the top 6) 
```{r}
quest5 <- filter(mtcar_data, cyl == 8)%>%
      arrange(cyl, -hp)%>%
      select(name, cyl, hp)%>%
      head()
quest5
```
6. Produce a table of fuel efficiency (mpg) for 4-cylinder cars ranked best to worst.
```{r}
quest6 <- filter(mtcar_data, cyl == 4)%>%
      arrange(cyl, -mpg)%>%
      select(name, cyl, mpg)
quest6
```
7. List the cars that have fuel efficiency (mpg) greater than or equal to 21 miles 
per gallon and horsepower (hp) greater than 100.
```{r}
quest7 <- filter(mtcar_data, mpg >= 21, hp>100)
quest7
#did not ask to sort by variable
```
8. What are the top 10 cars in ratio of horsepower (hp) to fuel-efficiency (mpg)?
```{r}
quest8 <- mutate(mtcar_data, ratio=hp/mpg) %>%
       arrange(-ratio) %>%
       slice(1:10) %>%
       select(name, ratio)
quest8
```
###############################################################
#Turn in a properly formatted script file for your answers. I am going to run the 
#entire script as one chunk of code, and if it doesn't work, I won't grade it. 
#You need to make it bullet-proof for your 'collaborator' (me). 
#Review Beckerman Section 3.3.5 for reference.
#OK to collaborate with others, but don't let people sponge off your hard work.
#Due one week from today (before class) via D2L Assignments submission box.